### 2019-06-05 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Changed \paragraph{XXX} to \paragraph{XXX.}
Fixed a bug of using subfloat and having long captions in the List of Figures.

% ----------------------------------------------------------------------
% \subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
\paragraph{Notations}\label{sub:25:aggregation}

@@

% ----------------------------------------------------------------------
\paragraph{Explanations of \Aggr{} versus \ExpQ{} }\label{sub:25:Exp4}

@@

The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted.
It corresponds to the second point \eqref{eq:2:forSecondLogTLowerBound2} in Theorem~\ref{thm:2:secondLogTLowerBound}.
It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli}).

@@

% ----------------------------------------------------------------------
\paragraph{No theoretical guarantees}\label{sub:25:theory}

@@

% ----------------------------------------------------------------------
\paragraph{Conclusion about our \Aggr{} algorithm}\label{sub:25:conclusion}

>>>>

% ----------------------------------------------------------------------
% \subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
\paragraph{Notations.}\label{sub:25:aggregation}

@@

% ----------------------------------------------------------------------
\paragraph{Explanations of \Aggr{} versus \ExpQ{} .}\label{sub:25:Exp4}

@@

The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted.
It corresponds to the second case in Theorem~\ref{thm:2:secondLogTLowerBound}.
It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli}).

@@

% ----------------------------------------------------------------------
\paragraph{No theoretical guarantees.}\label{sub:25:theory}

@@

% ----------------------------------------------------------------------
\paragraph{Conclusion about our \Aggr{} algorithm.}\label{sub:25:conclusion}

### 2019-06-05 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Fixed a bug of using subfloat and having long captions in the List of Figures.

\begin{figure}[!b]
    \centering
    \subfloat[10\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    %
    \subfloat[30\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    %
    \vspace*{-10pt}
    \subfloat[50\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    %
    \subfloat[100\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    % FIXME use a shorter caption for the list of figures in Appendix of the thesis: it takes lots of lines to have these (a)...(d) shown in list of figures
    \caption[XXX Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.]{Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    \vspace*{-10pt}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \subfloat[10\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_10.eps}
    \label{fig:41:ch2_10}}
    %
    \subfloat[30\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_30.eps}
    \label{fig:41:ch2_30}}
    %
    \vspace*{-10pt}
    \subfloat[50\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_50.eps}
    \label{fig:41:ch2_50}}
    %
    \subfloat[100\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_100.eps}
    \label{fig:41:ch2_100}}
    \caption{Performance of the UCB bandit algorithm for the special case of uniform repartition of the static devices, when the proportion of intelligent devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:figure4appendix}
\end{figure}

>>>>

\begin{figure}[!b]
    \centering
    \subfloat[][10\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    %
    \subfloat[][30\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    %
    \vspace*{-10pt}
    \subfloat[][50\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    %
    \subfloat[][100\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    \caption{Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    \vspace*{-10pt}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \subfloat[][10\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_10.eps}
    \label{fig:41:ch2_10}}
    %
    \subfloat[][30\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_30.eps}
    \label{fig:41:ch2_30}}
    %
    \vspace*{-10pt}
    \subfloat[][50\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_50.eps}
    \label{fig:41:ch2_50}}
    %
    \subfloat[][100\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_100.eps}
    \label{fig:41:ch2_100}}
    \caption{Performance of the UCB bandit algorithm for the special case of uniform repartition of the static devices, when the proportion of intelligent devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:figure4appendix}
\end{figure}

### 2019-06-05 2-Chapters/5-Chapter/chapter5.tex
Changed \paragraph{XXX} to \paragraph{XXX.}
Fixed a bug of using subfloat and having long captions in the List of Figures.

\paragraph{Abstract}
%
In this Chapter~\ref{chapter:5}, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature.
Using a decomposition of the centralized system regret, we start by explaining the intuition about what an efficient decentralized algorithm should do, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives order-optimal algorithms, that achieve state-of-the-art performance,
as illustrated by numerical simulations.
We conclude by reviewing different extensions of the multi-player models.

@@

\paragraph{Publications}

@@

\begin{table}[ht]
    % \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized Multiple play \klUCB{} & $\mathbf{91 \pm 21}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0 \pm 0}$ \\
        \Selfish-\klUCB{} & $249 \pm 35$ & $728 \pm 94$ & $2953 \pm 501$ \\
        \hline
        \textsc{Sic-MMAB} & $1705 \pm 340$ & $3915 \pm 300$ & $1713 \pm 52$ \\
        Improved \MusicalChair{} & $\textcolor{red}{12149 \pm 60}$ & $\textcolor{red}{22341 \pm 77}$ & $\textcolor{red}{27462 \pm 85}$ \\
        \hline
    \end{tabular}
    % \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, for the ``no sensing'' case.}
    \caption{Comparison for different algorithms on the same problem with $M=3,6,9$ players, for the ``no sensing'' case. We give the mean regret $\pm$ $1$ std-dev, and more work is needed on our implementation on Improved \MusicalChair. The results on \textsc{Sic-MMAB} appear to confirm the numerical experiments in the paper \cite{BoursierPerchet18}.}
    \label{table:5:meanRegretSimulationsNoSensing}
% \end{footnotesize}
\end{table}

@@

% DONE run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        \hline
        \rhoLearn-\klUCB{} + \klUCB{} & $546 \pm 190$ & $1172 \pm 295$ & $1416 \pm 347$ \\
        \rhoLearn-\klUCB{} + Bayes-UCB & $561 \pm 219$ & $1204 \pm 394$ & $1363 \pm 331$ \\
        \rhoLearn-\klUCB{} + Exp3 & $529 \pm 175$ & $1659 \pm 331$ & $5134 \pm 976$ \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        \hline
    \end{tabular}
    \caption{Comparing \RhoRand{} and \rhoLearn{} on a simple MP bandit problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}

@@

% \paragraph{Acknowledgments}
% Thanks to Odalric-Ambrym Maillard at Inria Lille for useful discussions, and thanks to Christophe Moy at University Rennes 1.

>>>>

\paragraph{Abstract.}
%
In this Chapter~\ref{chapter:5}, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature.
Using a decomposition of the centralized system regret, we start by explaining the intuition about what an efficient decentralized algorithm should do, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives order-optimal algorithms, that achieve state-of-the-art performance,
as illustrated by numerical simulations.
We conclude by reviewing different extensions of the multi-player models.

@@

\paragraph{Publications.}

@@

\begin{table}[ht]
    % \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized Multiple play \klUCB{} & $\mathbf{91 \pm 21}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0 \pm 0}$ \\
        \Selfish-\klUCB{} & $249 \pm 35$ & $728 \pm 94$ & $2953 \pm 501$ \\
        \hline
        \textsc{Sic-MMAB} & $1705 \pm 340$ & $3915 \pm 300$ & $1713 \pm 52$ \\
        Improved \MusicalChair{} & $\textcolor{red}{12149 \pm 60}$ & $\textcolor{red}{22341 \pm 77}$ & $\textcolor{red}{27462 \pm 85}$ \\
        \hline
    \end{tabular}
    % \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, for the ``no sensing'' case.}
    \caption{Comparison for different algorithms on the same problem with $M=3,6,9$ players, for the ``no sensing'' case. We give the mean regret $\pm$ $1$ std-dev, and more work is needed on our implementation on Improved \MusicalChair. The results on \textsc{Sic-MMAB} appear to confirm the numerical experiments of \cite{BoursierPerchet18}.}
    \label{table:5:meanRegretSimulationsNoSensing}
% \end{footnotesize}
\end{table}

@@

% DONE run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        \hline
        \rhoLearn-\klUCB{} + \klUCB{} & $546 \pm 190$ & $1172 \pm 295$ & $1416 \pm 347$ \\
        \rhoLearn-\klUCB{} + Bayes-UCB & $561 \pm 219$ & $1204 \pm 394$ & $1363 \pm 331$ \\
        \rhoLearn-\klUCB{} + Exp3 & $529 \pm 175$ & $1659 \pm 331$ & $5134 \pm 976$ \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        \hline
    \end{tabular}
    \caption{Comparing \RhoRand{} and \rhoLearn{} on a simple MP-MAB problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}

@@

% \paragraph{Acknowledgments.}
% Thanks to Odalric-Ambrym Maillard at Inria Lille for useful discussions, and thanks to Christophe Moy at University Rennes 1.
